Detecting Facial Expressions in Video Stills from Professional Tennis Matches

### 2018-01-17 paper/paper.Rmd
Accessories table paragraph explanation

The use of accessories like glasses and head wear, visors or hats, is common during the Australian Open as play is mostly outdoors during daytime.  Table \@ref(tab:accessories) shows player use of head wear and glasses, as tagged manually.

of the proportions tells that of the faces wearing glasses, there were a similar amount of faces captured with and without head wear. Of those without glasses only 26% wore head wear. This may be influenced by weather and sunlight on the court during Australian Open matches.

@@

\begin{table}[htp]
%\parbox{.5\linewidth}{
\caption{Conditional proportions of faces of players wearing glassesor headwear or not, captured by the different software, as a proportion of the manually tagged faces. API's unaffected by glasses will have similar proportions for both categories. Animetrics had the biggest proportion difference, and thus, most affected. Google is the least affected.}
\bigskip
\label{tab:glassesheadwear}
\centering
\begin{tabular}{|l|rr|rr|}  \hline
& \multicolumn{2}{r|}{Headwear}&\multicolumn{2}{r|}{Glasses}\\\cline{2-5}
API & Yes & No & Yes & No \\\hline
Google & 0.48 & 0.69 & 0.43 & 0.60 \\
Microsoft & 0.19 & 0.32 & 0.14 & 0.26 \\
Skybiometry & 0.16 & 0.28 & 0.12 & 0.23 \\
Animetrics & 0.11 & 0.27 & 0.08 & 0.21 \\\hline
\end{tabular}
\end{table}

>>>>

The Australian Open conducts matches on a range of courts, as some of these courts are located outdoors it is common to see accessories worn by players. Glasses, visors, hats, sweatbands and other additional pieces are worn by players, especially during day matches played outside. Table \@ref(tab:accessories) shows the accessories associated with a manually tagged face. It can be seen that most faces captured were not wearing glasses, however there were a similar amount of faces captured with and without head wear.

@@

\begin{table}[ht]
%\parbox{.5\linewidth}{
\caption{Conditional proportions of faces of players wearing glasses or headwear or not, captured by the different software, as a proportion of the manually tagged faces. API's will have similar proportions for both categories if they are not affected by the presence of an accessory. Animetrics had the biggest proportion difference, and thus, most affected. Google is the least affected.}
\bigskip
\label{tab:glassesheadwear}
\centering
\begin{tabular}{|l|rr|rr|}  \hline
& \multicolumn{2}{r|}{Headwear}&\multicolumn{2}{r|}{Glasses}\\\cline{2-5}
API & Yes & No & Yes & No \\\hline
Google & 0.48 & 0.69 & 0.43 & 0.60 \\
Microsoft & 0.19 & 0.32 & 0.14 & 0.26 \\
Skybiometry & 0.16 & 0.28 & 0.12 & 0.23 \\
Animetrics & 0.11 & 0.27 & 0.08 & 0.21 \\\hline
\end{tabular}
\end{table}

The conditional proportions are interpretted as the proportion of faces found by the API, that were tagged manually and having the attributes that were tabulated. For example, the value in the first row and first column of table \@ref(tab:glassesheadwear) highlights that Google found 0.48, or 48%, of the faces found manually and tagged as wearing headwear. As the values in the row for Google are the largest amounts in each column, it found more of the manually tagged faces in any situation considered. The next best software, Microsoft, found less than half the amount of manually tagged faces that Google located.

Animetrics may have been impeded by the use of accessories as it located only 0.08, or 8%, of the faces tagged manually as wearing a hat or visor, and 0.11, or 11%, of the faces tagged manually as wearing glasses.
When acceories are not worn, the proportion of faces found are closer to the next best API, Skybiometry.
